### 2014-11-09 tex/precise.tex
adding the correct style file

The rewrite rules for check the equals true and equals false when
comparing two references in the symbolic summary heap is shown
in~\figref{fig:eqs}(a). First the equals reference true rewrite rule
returns true if two references $r_0$ and $r_1$ are equal. In GSE this
is a simple comparision of object refrences. In the symbolic summary
heap, however, there we campare sets of constraint location pairs for
each reference. We construct three sets of constraints (i)
$\Phi_\alpha$ constains combinations of constraints ($\phi_0 \wedge
\phi_1$) from $r_0$ and $r_1$

>>>>

The rewrite rules for check the equals true and equals false when
comparing two references in the symbolic summary heap is shown
in~\figref{fig:eqs}(a). First the equals reference true rewrite rule
returns true if two references $r_0$ and $r_1$ are equal. In GSE this
is a simple comparision of object refrences. In the symbolic summary
heap, however, there we campare sets of constraint location pairs for
each reference. We construct three sets of constraints. The first set,
$\Phi_\alpha$, we check whether under some constraints $\phi_0$ and
$\phi_1$ whether references $r_0$ and $r_1$ respectively point to the
same location $l$.  For all such constraints we create conjunctions of
the constraints $\phi_0 \wedge \phi_1$ and add them to set
$\Phi_\alpha$. The next set of constraints si $\Phi_0$ which contains
the set of constraints from $r_0$ that lead to $l$ such that there is
no constraints under which $r_1$ can point to that $l$.
